%-----------PROJECTS-----------%
\section{Projects}
\resumeSubHeadingListStart


    \resumeProjectHeading
    {\textbf{AI-Assisted Code Review Tool} $|$ \emph{Python, Flask, NLP, GitHub API, Docker}}    {}
    \resumeItemListStart
                \resumeItem{Developed an AI-assisted code review tool leveraging natural language processing to analyze code and generate review suggestions.}
        \resumeItem{Integrated with the GitHub API to automate comments on pull requests, significantly reducing code review time by 40%.}
        \resumeItem{Used Flask for backend services, ensuring scalability through Docker deployment.}
        \resumeItem{Collaborated with teams to continually refine NLP algorithms for improving code review accuracy.}

    \resumeItemListEnd
    
    \resumeProjectHeading
    {\textbf{Smart Traffic Control System} $|$ \emph{Python, OpenCV, Raspberry Pi, MQTT, TensorFlow}}    {}
    \resumeItemListStart
                \resumeItem{Designed an AI-powered traffic control system to analyze real-time video feeds, optimizing traffic flow using TensorFlow for vehicle classification.}
        \resumeItem{Implemented MQTT for communication between edge devices and a centralized server, demonstrating real-time data processing capabilities.}
        \resumeItem{The system's dynamic adjustments reduced simulated congestion by up to 25%, showcasing practical application of machine learning.}
        \resumeItem{Collaborated with a multidisciplinary team to integrate hardware and software components seamlessly.}

    \resumeItemListEnd
    
    \resumeProjectHeading
    {\textbf{Distributed Database Replication System} $|$ \emph{Java, Apache Kafka, MySQL, Docker, Kubernetes}}    {}
    \resumeItemListStart
                \resumeItem{Engineered a distributed database replication system via Apache Kafka, ensuring high availability across data centers.}
        \resumeItem{Utilized MySQL for data storage and managed container orchestration with Docker and Kubernetes, enhancing deployment efficiency.}
        \resumeItem{Implemented monitoring tools and conflict resolution strategies, significantly reducing downtime by 70%.}
        \resumeItem{Delivered a robust solution that successfully integrated with existing data workflows and infrastructure.}

    \resumeItemListEnd
    

\resumeSubHeadingListEnd
