%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart


    \resumeSubheading
    {Tech Corp}{Jan 2022 -- Dec 2022}
    {Software Engineer}{San Francisco, CA}
    \resumeItemListStart
        \resumeItem{Developed scalable web applications using Python and Django.}
        \resumeItem{Optimized database queries, improving performance by 30 percent.}
        \resumeItem{Designed and implemented RESTful APIs for client-server communication.}
        \resumeItem{Led a team of three engineers in developing a critical feature.}
        \resumeItem{Improved codebase maintainability by introducing linting and CI/CD pipelines.}
        \resumeItem{Performed code reviews and mentored junior engineers.}
        \resumeItem{Collaborated with cross-functional teams to deliver key milestones.}
        \resumeItem{Integrated third-party services to extend product capabilities.}
        \resumeItem{Documented best practices and created a comprehensive onboarding guide.}
        \resumeItem{Received company recognition for exceptional contribution to project timelines.}

    \resumeItemListEnd
    
    \resumeSubheading
    {InnoTech Solutions}{Feb 2021 -- Dec 2021}
    {Data Analyst}{Austin, TX}
    \resumeItemListStart
        \resumeItem{Analyzed large datasets using Python and SQL to identify trends.}
        \resumeItem{Automated reporting processes, reducing manual workload by 50 percent.}
        \resumeItem{Created dashboards in Tableau for real-time business insights.}
        \resumeItem{Cleaned and preprocessed data for machine learning models.}
        \resumeItem{Designed experiments to validate hypotheses and drove decision-making.}
        \resumeItem{Collaborated with engineering teams to ensure data integrity.}
        \resumeItem{Presented findings to stakeholders, influencing strategic plans.}
        \resumeItem{Optimized ETL pipelines for improved efficiency.}
        \resumeItem{Devised data validation scripts to enhance reporting accuracy.}
        \resumeItem{Contributed to the development of a predictive analytics platform.}

    \resumeItemListEnd
    
    \resumeSubheading
    {NextGen Software}{Jun 2020 -- Jan 2021}
    {Intern Software Developer}{Seattle, WA}
    \resumeItemListStart
        \resumeItem{Assisted in developing a customer-facing web application using React.}
        \resumeItem{Built reusable components to standardize UI design.}
        \resumeItem{Collaborated with the backend team to integrate APIs.}
        \resumeItem{Resolved over 50 bugs and implemented feature enhancements.}
        \resumeItem{Gained hands-on experience with Agile development processes.}
        \resumeItem{Wrote unit and integration tests to ensure code quality.}
        \resumeItem{Participated in design discussions and code reviews.}
        \resumeItem{Contributed to documentation for team handoffs.}
        \resumeItem{Created prototypes to test new concepts.}
        \resumeItem{Learned and applied Git best practices for version control.}

    \resumeItemListEnd
    
    \resumeSubheading
    {Global Tech Enterprises}{Mar 2019 -- May 2020}
    {IT Support Specialist}{New York, NY}
    \resumeItemListStart
        \resumeItem{Provided technical support for hardware and software issues.}
        \resumeItem{Installed and configured computer systems and applications.}
        \resumeItem{Diagnosed and resolved network connectivity problems.}
        \resumeItem{Maintained inventory of IT equipment and software licenses.}
        \resumeItem{Trained employees on new software and tools.}
        \resumeItem{Developed scripts to automate routine IT tasks.}
        \resumeItem{Documented troubleshooting procedures for common issues.}
        \resumeItem{Assisted in upgrading company servers and infrastructure.}
        \resumeItem{Monitored system performance and applied updates as needed.}
        \resumeItem{Collaborated with vendors to resolve product-related problems.}

    \resumeItemListEnd
    
\resumeSubHeadingListEnd
