%-----------EXPERIENCE-----------%
\section{Experience}
\resumeSubHeadingListStart


    \resumeSubheading
    {AI Ventures}{Jun 2020 -- Apr 2021}
    {Machine Learning Intern}{Chicago, IL}
    \resumeItemListStart
        \resumeItem{Developed deep learning models for image classification using PyTorch and TensorFlow, enhancing model accuracy by 15% through transfer learning techniques.}
        \resumeItem{Built and deployed REST APIs to serve machine learning predictions, ensuring robust end-user access.}
        \resumeItem{Conducted hyperparameter tuning and performance optimization for models, improving inference speed for real-time applications.}
        \resumeItem{Documented and presented results to stakeholders, translating complex technical findings into actionable insights.}

    \resumeItemListEnd
    
    \resumeSubheading
    {DataSys Solutions}{May 2021 -- Dec 2022}
    {Data Engineer}{Boston, MA}
    \resumeItemListStart
        \resumeItem{Built ETL pipelines to process terabytes of data using Apache Airflow and Spark, improving data ingestion efficiency by 50%.}
        \resumeItem{Designed data models for efficient storage and retrieval in a Snowflake data warehouse, optimizing query performance.}
        \resumeItem{Integrated machine learning models into data pipelines, delivering predictive insights and enhancing business analytics capabilities.}
        \resumeItem{Collaborated with data scientists and engineers to ensure seamless data integration and compliance with data quality standards.}

    \resumeItemListEnd
    
    \resumeSubheading
    {Tech Innovators Inc.}{Jan 2023 -- Present}
    {Full Stack Developer}{San Jose, CA}
    \resumeItemListStart
        \resumeItem{Designed and deployed responsive web applications using React, Node.js, and PostgreSQL, enhancing user interaction through data-driven design.}
        \resumeItem{Collaborated with cross-functional teams to implement GraphQL APIs, improving data-fetching efficiency and reducing overhead.}
        \resumeItem{Mentored junior developers in best practices for coding and debugging, fostering a collaborative learning environment.}
        \resumeItem{Participated in Agile development processes, ensuring timely delivery of project milestones.}

    \resumeItemListEnd
    
\resumeSubHeadingListEnd
